\documentclass[9pt,letterpaper,twocolumn]{extarticle}

\usepackage[top=0.45in, bottom=0.4in, left=0.45in, right=0.45in, headsep=6pt, footskip=12pt]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}

\definecolor{ac}{HTML}{0077B6}
\definecolor{mg}{HTML}{666666}

\titleformat{\section}{\normalsize\bfseries\color{ac}}{}{}{}[\vspace{-2pt}]
\titlespacing*{\section}{0pt}{5pt}{2pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{ac}\leaders\hrule height \headrulewidth\hfill}}
\fancyhead[L]{\scriptsize\textbf{\textcolor{ac}{SIQUR}} \textcolor{mg}{$|$ Technical Memo}}
\fancyhead[R]{\scriptsize\textcolor{mg}{April 2026}}
\fancyfoot[C]{\scriptsize\textcolor{mg}{See everything. Miss nothing.}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlength{\columnsep}{14pt}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
\setlength{\abovedisplayshortskip}{2pt}
\setlength{\belowdisplayshortskip}{2pt}
\setlist{nosep, leftmargin=1em}

\begin{document}

\twocolumn[{%
\begin{center}
\vspace{-4pt}
{\Large\bfseries\textcolor{ac}{SIQUR}}\\[2pt]
{\small Optimal Camera Placement, 3D Spatial UI, and Crowdsourced Forensic Intelligence}\\[4pt]
{\scriptsize\textcolor{mg}{R.\ Muppa \quad D.\ Chen \quad M.\ Chauhan \quad D.\ Wang \quad R.\ Indupuri \quad$\cdot$\quad Purdue University}}\\[3pt]
\textcolor{ac}{\rule{\textwidth}{0.4pt}}
\end{center}
\vspace{4pt}
}]

\section*{The Problem}

Over 1 billion CCTV cameras are deployed worldwide, yet placement relies on installer intuition rather than mathematical optimization. The result: predictable blind spots, wasted hardware budgets, and zero feedback from post-incident review back into system design. SIQUR closes this loop with three integrated components: \textbf{(1)}~mathematically optimal camera placement via combinatorial optimization, \textbf{(2)}~a photorealistic 3D spatial interface built on Gaussian splatting for immersive tactical awareness, and \textbf{(3)}~OpenClaw, a crowdsourced forensic annotation protocol that converts community investigation into ML training data.

\section*{Camera Placement Model}

We formalize camera placement as a 3D variant of the \emph{Art Gallery Problem} (Chv\'{a}tal, 1975), which proves that $\lfloor n/3 \rfloor$ guards always suffice to cover a simple polygon with $n$ vertices. For a building polytope $\mathcal{P} \subset \mathbb{R}^3$, we discretize the interior into a coverage grid $G = \{g_1, \ldots, g_n\}$ and define candidate camera positions $C = \{c_1, \ldots, c_m\}$ on wall surfaces at mounting height $h = 2.5$\,m. Each camera $c_i$ has pose parameters $\boldsymbol{\theta}_i = (\phi, \psi, \alpha, r)$ representing yaw, pitch, field-of-view angle, and effective range. The \textbf{visibility function} is defined as:
%
\begin{equation}
v(c_i, g_j) = \begin{cases} 1 & \|c_i - g_j\| \leq r \;\wedge\; \angle(c_i, g_j) \leq \frac{\alpha}{2} \;\wedge\; \text{clear}(c_i, g_j) \\ 0 & \text{otherwise} \end{cases}
\end{equation}
%
where $\text{clear}(c_i, g_j)$ denotes an unoccluded line of sight, verified via raycasting against $\mathcal{P}$. The placement objective reduces to a \textbf{Maximum Coverage Location Problem}, equivalent to weighted Set Cover and therefore NP-hard (Feige, 1998):
%
\begin{equation}
\max_{S \subseteq C,\; |S| \leq k} \;\; \mathcal{C}(S) = \sum_{j=1}^{n} w_j \cdot \mathbb{1}\Big[\exists\, c_i \in S : v(c_i, g_j) = 1\Big]
\end{equation}
%
where $w_j$ is the priority weight of grid point $j$ (elevated near building entries, high-traffic corridors, and asset zones), and $k$ is the user-specified camera budget. The standard greedy algorithm achieves an approximation ratio of $(1 - 1/e) \approx 0.632$. We augment this with a \textbf{genetic algorithm} (Yildiz et al., 2014) operating on binary chromosomes $\mathbf{x} \in \{0,1\}^m$ with fitness function:
%
\begin{equation}
f(\mathbf{x}) = \frac{\sum_{j} w_j \cdot \mathbb{1}\big[\exists\, i : x_i = 1 \,\wedge\, v(c_i, g_j) = 1\big]}{\sum_{j} w_j} - \lambda \max\big(0,\, \|\mathbf{x}\|_1 - k\big)
\end{equation}
%
with tournament selection, single-point crossover ($p_c = 0.8$), bit-flip mutation ($p_m = 0.02$), converging within ${\sim}200$ generations. The output coverage ratio $\rho \in [0,1]$ is surfaced to the user as a placement quality metric.

\section*{3D Spatial Interface}

Building environments are captured via photogrammetry and represented as \textbf{3D Gaussian Splats} (Kerbl et al., SIGGRAPH 2023). Each scene primitive $\mathcal{G}_k$ is parameterized by position $\boldsymbol{\mu}_k$, covariance $\boldsymbol{\Sigma}_k$, opacity $\alpha_k$, and spherical harmonic color $\mathbf{c}_k$. The rendered pixel color is computed via differentiable alpha compositing:
%
\begin{equation}
C(\mathbf{p}) = \sum_{k=1}^{K} \mathbf{c}_k \, \alpha_k \prod_{j=1}^{k-1}(1 - \alpha_j) \cdot \exp\!\left(-\tfrac{1}{2}\Delta\mathbf{p}_k^\top \boldsymbol{\Sigma}_k'^{-1} \Delta\mathbf{p}_k\right)
\end{equation}
%
where primed quantities denote 2D screen-space projections. This enables real-time rendering at ${>}30$\,fps with sub-centimeter visual fidelity, allowing operators to navigate any placed camera's exact viewpoint. A Mapbox GL satellite layer provides global context, with cinematic iris-wipe transitions from orbital zoom to building interior.

\section*{OpenClaw: Crowdsourced Forensics}

After an incident, relevant camera feeds are exposed through OpenClaw, a structured crowdsourced investigation interface. Community participants annotate temporal segments, tag persons of interest, and flag anomalous events. Each annotation is a tuple $(t, \mathbf{b}, \ell, p_u)$: timestamp, bounding box, semantic label, and annotator confidence. Following the dual-use computation paradigm (von Ahn et al., 2008), consensus labels are computed as:
%
\begin{equation}
\hat{\ell}_t = \arg\max_{\ell} \sum_{u \in U_t} p_u \cdot \mathbb{1}[\ell_u = \ell]
\end{equation}
%
High-agreement annotations feed a continual learning pipeline for anomaly detection models, creating a \textbf{flywheel}: more incidents analyzed $\to$ better training data $\to$ stronger models $\to$ fewer blind spots $\to$ faster resolution.

\section*{Architecture}

\vspace{2pt}
{\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Component} & \textbf{Technology} \\
\midrule
Placement Engine & OR-Tools + GA, Python, FastAPI \\
3D Scene Rendering & Gaussian Splatting, Three.js \\
Satellite Globe & Mapbox GL \\
Frontend & Next.js, Framer Motion \\
Video Simulation & Qwen 2.5, NVIDIA DGX \\
\bottomrule
\end{tabular}}

\vspace{6pt}
\noindent\textcolor{ac}{\rule{\columnwidth}{0.3pt}}

\vspace{2pt}
{\scriptsize\textbf{References}\par\vspace{1pt}
\noindent [1] Chv\'{a}tal, \textit{J.\ Comb.\ Theory B}, 1975.\;
[2] Feige, \textit{J.\ ACM}, 1998.\;
[3] Kerbl et al., \textit{ACM TOG}, 2023.\;
[4] Yildiz et al., \textit{IEEE Trans.\ Comp.}, 2014.\;
[5] von Ahn et al., \textit{Science}, 2008.\par}

\end{document}
